%-------------------------
% Resume in LaTeX
% Professional, no color, no decorative elements
%-------------------------

\documentclass[11pt,letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage{charter}                 % clean, classic, professional serif typeface
\usepackage[top=0.7in,bottom=0.7in,left=0.8in,right=0.8in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\tabcolsep}{0pt}
\setlength{\parindent}{0pt}
\raggedbottom
\raggedright

\urlstyle{same}

%-------------------------------------------
% Section formatting: bold heading + thin rule, no color, no small caps font issues
\titleformat{\section}
  {\normalfont\bfseries\large}
  {}{0em}{}
  [\vspace{-7pt}\rule{\linewidth}{0.6pt}]
\titlespacing{\section}{0pt}{13pt}{6pt}

%-------------------------------------------
% List spacing (replaces manual negative \vspace hacks with consistent rules)
\setlist[itemize,1]{leftmargin=0pt, label={}, itemsep=10pt, topsep=3pt, parsep=0pt, partopsep=0pt}
\setlist[itemize,2]{leftmargin=14pt, label=\textendash, itemsep=3pt, topsep=3pt, parsep=0pt, partopsep=0pt, after=\vspace{4pt}}

%-------------------------------------------
% Custom commands
\newcommand{\resumeItem}[2]{%
  \item \textbf{#1}{ #2}%
}

\newcommand{\resumeSubheading}[4]{%
  \item
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{\normalsize #1} & \textit{\small #2} \\
    \textit{#3} & \small #4 \\
  \end{tabular*}%
}

\newcommand{\resumeSubheadingTwo}[6]{%
  \item
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{\normalsize #1} & \textit{\small #2} \\
    \textit{#3} & \small #4 \\
    \textit{#5} & \small #6 \\
  \end{tabular*}%
}

\newcommand{\resumeSubheadingTree}[8]{%
  \item
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{\normalsize #1} & \textit{\small #2} \\
    \textit{#3} & \small #4 \\
    \textit{#5} & \small #6 \\
    \textit{#7} & \small #8 \\
  \end{tabular*}%
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

% Highlighted (but not flashy) Technologies/Domains lines: uppercase bold label, no italics, aligned values
\newcommand{\resumeTechDomain}[2]{%
  \item[]\vspace{2pt}
  \makebox[3.4cm][l]{\textbf{\small TECHNOLOGIES}}#1\\[3pt]
  \makebox[3.4cm][l]{\textbf{\small DOMAINS}}#2
  \vspace{2pt}%
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\small

%----------HEADING-----------------
\begin{center}
  {\LARGE \textbf{Bruna Zamith Santos}}\\[2pt]
  {\normalsize PhD Candidate}\\[6pt]
  \href{mailto:bruna.zamith@hotmail.com}{bruna.zamith@hotmail.com}
  \,\textbar\,
  +55 (12) 99166-7541
  \,\textbar\,
  \href{http://bzamith.github.io}{bzamith.github.io}
  \,\textbar\,
  \href{https://linkedin.com/in/bruna-zamith/}{linkedin.com/in/bruna-zamith}
\end{center}
\vspace{2pt}

% %-----------AREAS OF INTEREST-----------------
% \section{Main Areas of Interest}
% \resumeSubHeadingListStart
%     \resumeSubItem{Data Science, Machine Learning, Research \& Development, Software Engineering}{}
% \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart
    \resumeSubheading{iFood}{Remote - Brazil}
        {Staff Data Scientist}{Dec. 2025 -- Current}
    \resumeItemListStart
        \resumeItem{}{Develop recommendation models and bidding optimization systems for Retail Media and Ads products.}
        \resumeItem{}{Own end-to-end ML development: business framing, experimentation, model training, deployment, monitoring, and optimization.}
        \resumeTechDomain{AWS, Python, SQL}{Recommender Systems, Optimization, GenAI, A/B Testing, MLOps}
    \resumeItemListEnd

    \resumeSubheadingTwo{Amazon}{Remote - Brazil}
        {Applied Scientist II}{Feb. 2024 -- Dec. 2025}
        {Data Scientist II}{Mar. 2022 -- Jan. 2024}
    \resumeItemListStart
        \resumeItem{}{Own end-to-end supervised ML for Catalog and Supply Chain: business framing, data/feature pipelines, model training, offline and online evaluation, deployment, monitoring, and MLOps.}
        \resumeItem{}{Delivered models credited with \$50M+ incremental revenue and enabling 1.3M+ new catalog product launches through scalable decisioning services and data products.}
        \resumeItem{}{Partnered with PM/Eng/Ops to prioritize a multi-quarter roadmap, negotiate trade-offs (latency/cost/quality), and unblock adoption across LatAm businesses.}
        \resumeItem{}{Program Owner, GenAI capacitation: designed curriculum and delivered trainings and office hours for different job roles across 12 marketplaces (10k+ employees); measured adoption and learning outcomes.}
        \resumeItem{}{Published 2 internal Amazon papers (applied ML/GenAI); evangelized best practices in experimentation, evaluation, and productionization.}
        \resumeTechDomain{AWS, Python, SQL, Typescript}{GenAI, Forecasting, Classification, A/B Testing, MLOps}
    \resumeItemListEnd

    \resumeSubheadingTree{Amazon}{Sao Paulo, SP - Brazil}
        {Software Development Engineer II}{Dec. 2021 -- Feb. 2022}
        {Software Development Engineer I}{Jul. 2020 -- Nov. 2021}
        {Software Development Intern}{Jan. 2020 -- Jul. 2020}
    \resumeItemListStart
        \resumeItem{}{Built and operated large-scale front-/back-end services integrating with Amazon core systems to improve seller \& buyer experiences.}
        \resumeItem{}{Led design reviews, API contracts, performance testing, reliability, and on-call for high-throughput workloads.}
        \resumeItem{}{Shipped resilient, well-instrumented services adopted by core retail flows in Brazil.}
        \resumeTechDomain{AWS, Java, Python, Typescript}{Distributed Systems, APIs, Observability, Reliability}
    \resumeItemListEnd

    \resumeSubheading{Serasa Experian}{Sao Carlos, SP - Brazil}
        {MIS Intern}{Aug. 2019 -- Dec. 2019}
    \resumeItemListStart
        \resumeItem{}{Delivered Finance dashboards and automated data pipelines; improved reporting accuracy and turnaround time by 40\%.}
        \resumeTechDomain{SQL, SAS, Tableau}{Business Intelligence, Data Engineering}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education \& Research}
\resumeSubHeadingListStart
    \resumeSubheading{Federal University of Pernambuco (UFPE)}{Remote -- Brazil}
        {PhD in Artificial Intelligence}{Feb. 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Topic:}{Explainable AI (XAI) for Time Series Classification.}
        \resumeItem{GPA:}{10/10}
        \resumeTechDomain{Python (PyTorch/NumPy/Pandas), LaTeX}{XAI, Time Series, Instance Hardness}
    \resumeItemListEnd

    \resumeSubheading{Federal University of Sao Carlos (UFSCar)}{Remote - Brazil}
        {Masters in Artificial Intelligence}{Aug. 2021 -- Dec. 2023}
    \resumeItemListStart
        \resumeItem{Project:}{Climate Variables Forecasting \& Forest Fire Risk Classification in the Brazilian Pantanal. Pantanal faces recurrent fires driven by climate; existing indexes are biome-agnostic, limited in variables, and lack multi-day predictions.}
        \resumeItem{Approach:}{Built a two-stage ML system: (1) forecast climate variables; (2) classify daily fire-risk levels using predicted covariates. Compared exhaustive hyperparameter search to Genetic Algorithms (GA) for multi-objective optimization.}
        \resumeItem{Results:}{System outperformed standard fire-risk indexes on key classes and enabled forward-looking risk.}
        \resumeItem{GPA:}{10/10}
        \resumeTechDomain{Python, R}{Time Series, Forecasting, Classification, Genetic Algorithms}
    \resumeItemListEnd

    \resumeSubheading{Katholieke Universiteit Leuven (KU Leuven)}{Kortrijk, Flanders - Belgium}{Research Intern}{Sep. 2017 -- Dec. 2017}
    \resumeItemListStart
        \resumeItem{Project:}{Predicting Protein Functions via Interaction Prediction. Funded by Sao Paulo Research Foundation (FAPESP).}
        \resumeItem{Approach:}{Modeled protein function prediction as Hierarchical Multi-label Classification (HMC) over interaction networks; implemented data processing and evaluation pipelines.}
        \resumeItem{Outcome:}{Delivered reproducible code and benchmarks; informed subsequent HMC research at BioMaL/KU Leuven.}
        \resumeTechDomain{Java}{HMC, Bioinformatics}
    \resumeItemListEnd

    \resumeSubheading{Federal University of Sao Carlos (UFSCar)}{Sao Carlos, SP - Brazil}
        {Bachelor in Computer Engineering}{Mar. 2015 -- Jul. 2020}
    \resumeItemListStart
        \resumeItem{GPA:}{8.75/10}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\noindent
\begin{minipage}[t]{0.48\textwidth}
%-----------PROGRAMMING SKILLS-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages:}
      {Python (6 years); Java (5 years); SQL (3 years); Typescript (2 years); R (2 years); C++ (6 months)}
    \resumeSubItem{Others:}
      {AWS, Git, Linux, LaTeX}
  \resumeSubHeadingListEnd
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
%-----------LANGUAGE-----------------
\section{Language}
  \resumeSubHeadingListStart
    \resumeSubItem{Portuguese:}
      {Native}
    \resumeSubItem{English:}
      {Fluent (Cambridge English Certificate ESOL Intl)}
  \resumeSubHeadingListEnd
\end{minipage}

%-----------PUBLICATIONS-----------------
\section{Presentations, Proceedings, and Papers}
  \begingroup\small
  \begin{itemize}[leftmargin=0pt, label={}, itemsep=6pt, topsep=2pt, parsep=0pt, partopsep=0pt]
    \resumeSubItem{TSCFEval: A Model-Agnostic Framework for Evaluating Time Series Classification Counterfactuals}
    {B. Zamith Santos, M. F. Andrade Lira, R. Cerri. 2026. In \textit{Explainable Artificial Intelligence (XAI World Conference)}.}

    \resumeSubItem{A New Time Series Framework for Forest Fire Risk Forecasting and Classification}
    {B. Zamith Santos, B. Soriano, M. Narciso, D. Furtado, R. Cerri. 2023. In \textit{International Joint Conference on Neural Networks (IJCNN)}.}

    \resumeSubItem{Predictive Bi-Clustering Trees for Hierarchical Multi-Label Classification}
    {B. Zamith Santos, K. F. Nakano, R. Cerri, C. Vens. 2020. In \textit{European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (ECML-PKDD)}.}

    \resumeSubItem{Strategies for Selection of Positive and Negative Instances in the Hierarchical Classification of Transposable Elements}
    {B. Zamith Santos, T. G. Pereira, K. F. Nakano, R. Cerri. 2018. In \textit{Brazilian Conference on Intelligent Systems (BRACIS)}.}

    \resumeSubItem{A Genetic Algorithm for Transposable Elements Hierarchical Classification Rule Induction}
    {T. G. Pereira, B. Zamith Santos, R. Cerri. 2018. In \textit{IEEE Congress on Evolutionary Computation (IEEE CEC)}.}

    \resumeSubItem{A New Machine Learning Dataset for Hierarchical Classification of Transposable Elements}
    {B. Zamith Santos, R. Cerri. 2016. In \textit{National Meeting on Artificial and Computational Intelligence (ENIAC)}.}

    \resumeSubItem{Decision Trees for Hierarchical Classification of Transposable Elements}
    {B. Zamith Santos, R. G. Mantovani, L. Schietgat, C. Vens, R. Cerri. 2016. In \textit{Proceedings of the 25th Belgian-Dutch Machine Learning Conference (Benelearn)}.}
  \end{itemize}
  \endgroup

%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \begingroup\small
  \begin{itemize}[leftmargin=0pt, label={}, itemsep=6pt, topsep=2pt, parsep=0pt, partopsep=0pt]
    \resumeItem{\href{https://drive.google.com/file/d/1CwHMRyzeZmDvrS_AfFiSRuisy2ZotFBx/view}{Statistics and Optimization for Data Science and Operations Research (2026):}}{60 hours online course provided by University of Sao Paulo (USP).}
    \resumeItem{\href{https://coursera.org/share/43e3090b53acbdb77301e0ec5c6bbb81}{Recommender Systems Specialization (2025):}}{80 hours online course provided by University of Minnesota.}
    \resumeItem{\href{https://drive.google.com/file/d/1KvUsgIFlltR3SW48f4Pu1RNp0cE1g_y0/view?usp=sharing}{Fundamentals of Probability and Statistics for Data Science (2025):}}{30 hours online course provided by University of Sao Paulo (USP).}
    \resumeItem{\href{https://learn.deeplearning.ai/accomplishments/3db9d146-093c-4dea-bb10-35f1f4fcf390?usp=sharing}{Practical Multi AI Agents and Advanced Use Cases with crewAI (2025):}}{3 hours online course provided by DeepLearning.ai and crewAI.}
    \resumeItem{\href{https://coursera.org/share/236b7e6ee1cd2fe7d370d22032c9829b}{Practical Time Series Analysis (2024):}}{25 hours online course provided by The State University of New York (SUNY).}
    \resumeItem{\href{https://coursera.org/share/2c0b8bc9c80337baff021341eb7291f6}{Generative AI with Large Language Models (2024):}}{16 hours online course provided by DeepLearning.ai and Amazon Web Services (AWS).}
    \resumeItem{\href{https://coursera.org/share/bfeeaa2fdb5d0af4a6ae16bbea2308a5}{Sequence Models (2022):}}{38 hours online course provided by DeepLearning.ai.}
    \resumeItem{\href{https://coursera.org/share/26abd334d3e6eeb10cdef24a925c1a06}{Sequences, Time Series and Prediction (2022):}}{23 hours online course provided by DeepLearning.ai.}
    \resumeItem{\href{https://verify.acloud.guru/40ACAB21F4F9}{Introduction to AWS (2020):}}{5 hours online course provided by A Cloud Guru.}
    \resumeItem{\href{https://coursera.org/share/0f7a200acafda161712761aabc647fdf}{Version Control With Git (2019):}}{12 hours online course provided by Atlassian.}
    \resumeItem{\href{https://coursera.org/share/49e36f73ee5af2e58a65943a26848b88}{Software Development Processes and Methodologies (2019):}}{18 hours online course provided by University of Minnesota.}
  \end{itemize}
  \endgroup

\end{document}